Interactive results review

### 2024-08-05 nbs/guides/interactive/interactive.qmd
docs(nbs): write data tables to files
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

>>>>

### Save data files

We may also want to write data tables to review. Here we save the parameter
posterior distribution table

```{python}
# | label: save-parameter-posterior-mean-dataframe
from pyrovelocity.utils import save_parameter_posterior_mean_dataframe

save_parameter_posterior_mean_dataframe(
    adata=adata,
    input_dict=posterior_samples,
    dataframe_path="gene_parameter_posterior_mean.csv",
)
```

and the gene selection table

```{python}
# | label: save-gene-selection-table
posterior_samples["gene_ranking"].to_csv("gene_ranking.csv")
posterior_samples["gene_ranking"]
```
